---
title: "Homework 1"
author: "Alexis Colangelo"
date: "9/19/2019"
output: github_document
---

```{r_setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

### Creating specified data frame with:
* a random sample of size 8 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 8
* a factor vector of length 8, with 3 different factor “levels”

```{r, include=FALSE}
library(tidyverse)
```

```{r}
set.seed(2)

  problem1_df = tibble(
    rand_number = rnorm(8, mean = 0, sd = 1),
    vec_logical = c(rand_number > 0),
    vec_char = c("one", "two", "three", "four", "five", "six", "seven", "eight"),
    vec_factor = factor(c("low", "high", "low", "medium", "high", "medium", "high", "medium"))
    )
```
### Taking the mean of each variable in data frame:

* The mean of rand_number is `r mean(pull(problem1_df, rand_number))`
* The mean of vec_logical is `r mean(pull(problem1_df, vec_logical))`
* The mean of vec_char is `r mean(pull(problem1_df, vec_char))`
* The mean of vec_factor is `r mean(pull(problem1_df, vec_factor))`

##### The rand_number mean and vec_logical mean both worked, while the vec_char and vec_factor means did not work. Means can only be calculated for numeric and logical variables.

### Applying the as.numeric function to the logical, character, and factor variables: 
```{r, eval = FALSE}
as.numeric(pull(problem1_df, vec_logical))
as.numeric(pull(problem1_df, vec_char))
as.numeric(pull(problem1_df, vec_factor))
```
##### Both the logical and factor variables produced numeric values when the numeric function was applied, while the character variable introduced NA for all values. This happens because the character variable has values that are all unique while the logical has 2 possible values and the factor variable has 3 possible levels. It helps explain why a mean was not able to be calculated for the character value. 

Convert the logical vector to numeric, and multiply the random sample by the result:
```{r}

as.numeric(pull(problem1_df, vec_logical) * pull(problem1_df, rand_number)) 

```
Convert the logical vector to a factor, and multiply the random sample by the result:
```{r}

as.factor(pull(problem1_df, vec_logical) * pull(problem1_df, rand_number)) 

```
Convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result
```{r}
as.factor(pull(problem1_df, vec_logical))
as.numeric(pull(problem1_df, vec_logical) * pull(problem1_df, rand_number))
```

## Problem 2
Creating Data Frame
```{r}
set.seed(3)

  problem2_df = tibble(
    x = rnorm(500, mean = 0, sd = 1),
    y = rnorm(500, mean = 0, sd = 1),
    vec_logical = c(x + y > 1),
    vec_numeric = as.numeric(vec_logical),
    vec_factor = as.factor(vec_logical)
    
  )
  
    ```



  
  
  
  
  
  
  
  
  

#